Towards Reliable Machine Learning Deployments in the Cloud

### 2023-12-14 paper.tex

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{multirow}
\usepackage{hyperref}

@@

\section{Introduction}
\subsection{Motivations}
% \begin{itemize}
%     % \item \textbf{BIG} Data is the trend
%     % \item Costs are astronomical
%     \item Prevailing regulatory framework is clear about the robustness requirements, documented software changes, and explainable processes.
%     \item Other work relies on unreliable test/train split methodology
%     \item Which means that cars, medical equipment is tested in the wild
% \end{itemize}

Recently, machine learning using neural networks has become a popular way to classify large amounts of data---with applications ranging from medical imaging~\cite{ai_medical_imaging} to aviation~\cite{ai_aviation} and from security~\cite{ai_security,ai_luggage,ai_prison} to self-driving cars~\cite{ai_automotive}. However, neural networks need large amounts of data\cite{desislavov2021compute,bailly2022effects} to train ever-larger model~\cite{desislavov2021compute}, yielding increasingly marginal gains on test-set accuracy~\cite{sun2017revisiting}. Furthermore, popular models like Generative Pre-trained Transformer (GPT)\cite{floridi2020gpt} or ResNet~\cite{resnet} have many millions of parameters, requiring equally large training datasets. Media reports place the cost of training a large language model somewhere between 4 and 63 million dollars~\cite{}, meaning only a few entities in the whole world have the requisite hardware and/or cloud budget to build a competing system. Facebook's large language model, dubbed LLaMA, was placed on the codesharing website, GitHub~\cite{llama}. Immediately, an open-sourced clone was created, which itself spawned hundreds of offshoot projects~\cite{openllama}. The newest version of this open-source large language model (LLM) is able to outperform the commercially available GPT-3.5 model with a fraction of the parameters (13 Billion), small enough to run on a laptop without a graphics processing unit (GPU)~\cite{liu2023goat}. Given the immense cost of deploying modern neural networks, the required number of test samples creates serious questions about the efficacy of the typical train/test split methodology for evaluating the ability of a model to generalize beyond a training set~\cite{meyers} since regulatory standards around safety-critical software applications~\cite{IEC61508,iso26262,aviation_software,safetyframework} clearly define the maximum failure rate to be between $[1e-12, 1e-15]$ depending on the number of lives at risk ~\cite{iso26262}. Collecting, labelling, and testing a new set of data for every software change-as required by law would be prohibitively expensive. Therefore, a new evaluation methodology is required. As such, we propose an evaluation metholodgy, centered around survival analysis, which tests a model against `worst-case' input to verify the efficacy of one of modelling deployment decision over another. Then, we use this method to examine and minimize the deployment cost for a singule model architecture, measuring this in terms of both power and monetary cost. In short, our goal is to answer three questions,

\subsection{Research Questions}
Our goal is to answer the following three questions:
\begin{itemize}
    \item What is the relationship between latency, robustness, and deployment cost?
    \item What is the cheapest way to guarantee a certain response time and accuracy?
    \item Does better hardware lead to better models?
\end{itemize}

However, before we can answer these questions, we need to model the asymptotic behavior of various architectural choices, develop a method for precisely measuring model performance without resorting to trillions of test samples, and find a metric (or metrics) that will set one model apart from the others with respect to both failure rate and deployment cost.

\subsection{Contributions}
\begin{itemize}
    \item We confirm previous work about the efficacy of adversarial analysis for model selection.
    \item We measure the power and monetary cost of deploying a model across three different hardware architectures.
    \item We combine survival analysis with adversarial analysis to build accelerated failure models to compare the effect of model parameter choices.
    \item We use a Tree Parzen Estimator to minimize deployment cost while maximizing accuracy.
    \item Show that smaller models running on smaller hardware is far more cost effective, especially in the context of adversarial robustness.
\end{itemize}

\section{Background}
Machine learning pipelines play a crucial role in the development and deployment of robust and accurate models. However, managing complex pipelines across diverse CPU and GPU architectures, ensuring robustness against adversarial attacks, and understanding the relationship between computational cost, model loss, and prediction accuracy remain ongoing challenges. In this paper, we present a comprehensive study on leveraging Kubernetes~\cite{k8s} to manage a complex machine learning pipeline. We explore the robustness of the pipeline under adversarial attacks and examine the impact of computational cost on model performance in both benign and adversarial contexts.

Machine learning applications have witnessed tremendous growth in recent years, addressing a wide range of domains and providing significant advancements in various fields \cite{li_general_2016, croce_reliable_2020, athalye_obfuscated_2018}. As these applications become more sophisticated, the need to efficiently manage the underlying machine learning pipeline arises. The pipeline involves a series of interconnected steps, including data preprocessing, model training, post-processing, and inference. Efficiently orchestrating these steps across diverse CPU and GPU architectures poses significant challenges in terms of scalability, resource allocation, and workload distribution.

To address these challenges, containerization and orchestration technologies have gained prominence in managing complex machine learning pipelines. Kubernetes, a widely adopted container orchestration platform, provides a scalable and flexible environment for deploying, scaling, and managing microservices-based applications. Its ability to handle heterogeneous hardware architectures and workload distribution across clusters makes it an ideal choice for managing the complex computational requirements of machine learning pipelines.

Furthermore, ensuring the robustness of machine learning  models against adversarial attacks has become a critical concern~\cite{adversarialpatch, carlini_towards_2017, croce_reliable_2020, hopskipjump, chakraborty2018adversarial, art2018}. Adversarial attacks aim to exploit vulnerabilities in models by introducing subtle modifications to data submitted to various stages of the ML pipeline, leading to misclassification or otherwise erroneous outputs. Evaluating the robustness of ML models against adversarial attacks is crucial to assess their reliability and performance in real-world scenarios. By subjecting the ML pipeline to carefully crafted adversarial inputs, we can measure its resilience and identify potential vulnerabilities.

Additionally, understanding the relationship between computational cost, model loss, and prediction accuracy is vital for optimizing the pipeline's performance. Balancing computational resources, time constraints, and accuracy requirements is a fundamental consideration in deploying machine learning models in production environments. By analyzing the impact of computational cost on model loss and accuracy metrics, we can gain insights into the trade-offs involved and make informed decisions to optimize the pipeline's efficiency.

In this paper, we present a comprehensive study that combines Kubernetes as the underlying infrastructure for managing a complex ML pipeline across a variety of CPU and GPU architectures. We can investigate the robustness of the pipeline against adversarial attacks and explore the relationship between computational cost, model loss, and  prediction accuracy in both benign and adversarial contexts. Our experiments and analysis provide valuable insights into the trade-offs and considerations when deploying machine learning models under varying computational constraints and adversarial conditions.

@@

\subsection{Cloud Architectures}
A \textbf{microservice} is the smallest component of a `cloud-native' software stack. In the context of machine learning, that might be a tool for either training, inference, pre-processing, sampling, or any other arbitrarily small part of the data pipeline. A microservice \textbf{mesh} is a network infrastructure or architectural pattern that provides a unified and scalable approach to managing communication between microservices in a distributed system. It serves as a dedicated layer that abstracts away the complexity of service-to-service communication, enabling efficient and reliable interactions among these services. A microservice mesh typically consists of a set of interconnected components or proxies deployed alongside the microservices within the system. These components facilitate various capabilities and functionalities essential for managing the communication between microservices. Kubernetes has become one of the largest open source projects on the code-sharing website Github \cite{k8s-size}, which provides a framework for managing, monitoring, and networking a self-scaling set of tools across arbitrary software and hardware architectures.

\subsection{Machine Learning Pipelines}
Machine Learning pipelines are often long-running and complex software tool-chains with many tunable hyperparameters. Managing, tracking, and controlling for various parameters is non trivial, but many management tools are available~\cite{dvc, hydra, k8s}. In general, a dataset is split into \textbf{training} and \textbf{test} sets. The training set is then used to determine the best configuration of a given model architecture on a given hardware architecture with the expectation that it will generalize both on the withheld test set and on new data generated by users via application programming interface (API) calls. To verify the training process, the test set validated against the \textit{inference} configuration of a model which may run on different hardware than the \textbf{training} configuration to reduce cost, latency, or power consumption.

@@

A classifier with model parameters, $\theta$, $K(x; \theta)$, drawn from a set of all possible hyper-parameters, $\Theta$, seeks to minimize\footnote{This can also be formulated as a maximization function without loss of generality.} an \textbf{objective} (or \textbf{loss}) \textbf{function} $L(y, \hat{y})$ for some samples, $x$, some true labels $y$, and some model output, $K(x)$, such that the optimal loss value, $L^*$ is:
\[
L^*(y, K(x, \theta)) = \mathrm{argmin}_{\theta \in \Theta} y - K(x, \theta).
\]
From here, we can find the optimal configuration of the classifier by selecting the one that minimizes loss. In the case of neural-networks, however, this is non-trivial as the number of tunable parameters is often measured in the millions. Instead of finding an analytical solution to this equation, we often rely on \textbf{stochastic gradient descent}, which iteratively shuffles the data before adjusting the model parameters, $\theta$, in the direction that minimizes the loss, $-\nabla L(y, K(x, \theta))$, after some number of \textbf{epochs} (iterative random sampling of the data), $m$, such that:
\begin{equation}
\theta_{m+1} := \theta_{m} - \eta \nabla_x L(y, K(x, \theta_m))
\label{eq:sgd}
\end{equation}
where $\eta$ is a \textbf{learning rate} that is tuned to the particular model.

\subsection{Learning Rate Selection}
\label{learning_rate}
\cm{TODO}
\begin{itemize}
    \item Much work has gone into this~\cite{}.
    \item A good learning rate will give us training times that are linear w.r.t sample size ~\cite{}
    \item Will depend on the batch size and number of epochs (define epochs) ~\cite{}
    \item The best batch size will depend on the memory bandwidth of the GPU~\cite{}
    \item That bandwidth is not guaranteed in on-demand cloud environments~\cite{}
    \item Hardware is charged by the hour, so minimizing training/inference times will reduce the costs of deployment.
\end{itemize}

\subsection{Adversarial Attacks}
\label{attacks}
In the context of machine learning, an adversarial attack refers to deliberate and malicious attempts to manipulate or exploit machine learning models. Adversarial attacks are designed to deceive or mislead the model's behavior by introducing carefully crafted input data that can cause the model to make incorrect predictions or produce undesired outputs. That is, a successful attack is one in which the model outputs on unperturbed data $\hat{y}$ are not the same as the model outputs on perturbed data, $x'$. That is \textbf{adversarial success} or \textbf{accelerated failure} is one in which:
\begin{equation}
\hat{y} \neq y^* = K(x', \theta)
\label{eq:adv_success}
\end{equation}
Additionally, we can measure the accuracy of the model when tasked with these adversarial samples, giving us a metric called \textbf{adversarial accurracy}. The goal of an adversarial attack is often to exploit vulnerabilities in the model's decision-making process or to probe its weaknesses. These attacks can occur during various stages of the machine learning pipeline, including during training, inference, or deployment.

\cm{This itemize section could be cut and reduced to a couple sentences.}
\begin{itemize}
    \item Evasion Attacks: These attacks aim to manipulate input data during the inference phase to deceive the model into misclassifying or ignoring certain inputs. Attackers carefully craft perturbations or modify the input features to mislead the model while still appearing similar to the original input \cite{biggio_evasion_2013, carlini_towards_2017, adversarialpatch, pixelattack, hopskipjump}.
    \item Poisoning Attacks: In poisoning attacks, the attacker intentionally injects malicious or manipulated training samples into the training dataset. The goal is to influence the model's behavior during training so that it learns to make incorrect predictions or exhibit unwanted behaviors when presented with specific inputs \cite{biggio_poisoning_2013, saha2020hidden}.
    \item Inference Attacks: These attacks exploit the model's output or responses to obtain sensitive information about the training data or other confidential details. By observing the model's predictions or confidence scores for carefully crafted inputs, attackers can extract information that should ideally be kept private \cite{chakraborty_adversarial_2018, orekondy2019knockoff}.
    \item Model Inversion Attacks: Model inversion attacks aim to infer sensitive information about the training data or proprietary model by exploiting the model's outputs. Attackers utilize the model's responses to iteratively reconstruct or approximate training examples that are similar to the ones used during training \cite{chakraborty_adversarial_2018, choquette2021label, li2021membership}.
\end{itemize}
One attack designed to induce failures as quickly as possible~\cite{fgm} works by applying noise to a set of samples, $x$, to generate adversarial examples, $x'$, such that:

\begin{equation}
x' = x + \eta \mathrm{~sgn~}(\nabla_x L(y, K(x, \theta))).
\label{eq:fgm}
\end{equation}
In essence, this is stochastic gradient \textit{ascent}, the opposite process from model training (stochastic gradient \textit{descent}).

@@

In the case of safety- or security-critical domains, considering the worst-case scenario is routine~\cite{}. Whether we discuss automotive safety~\cite{}, crytographic systems~\cite{}, or healthcare malpractice~\cite{}, a component, algorithm, or system is considered broken if the \textbf{failure rate} exceeds certain statistical thresholds. An order of magnitude more automotive accidents, security breaches, or deaths due to medical negligence would be unacceptable and, as such, these standards are non-negotiable. However, this would mean testing somewhere around $(10^6, 10^9)$ samples to justify every model change. This is just not computationally feasible. Instead, we can use adversarial failure analysis to improve the precision of our measurements while only using a small set of test-data.

\subsubsection{Accuracy}
The failure rate, denoted by $h$, refers to the percentage or proportion of examples that cause the targeted machine learning model to misclassify or produce incorrect outputs \cite{meyers}. It measures the vulnerability or susceptibility of the model to noise-induced failures. A higher failure rate indicates a higher rate of misclassifications or incorrect predictions, signifying a weaker model in terms of \textbf{robustness} against noise-induced failures. Throughout, we use the terminology \textbf{benign accuracy} to refer to the performance on the test set using unperturbed data. The benign accuracy is defined as
\begin{equation}
 \mathrm{Accuracy} = 1 - \frac{\mathrm{False~Classifications}}{\mathrm{Total~Classifciations}}
\label{eq:acc}
\end{equation}
which is generally assumed to indicate the rate of failures in real-world data drawn from the same distribution as the test data \cite{}. However, the normal test/train split methodology consistently overestimates the model's performance in the presence of adversarial noise~\cite{croce_reliable_2020}. Additionally, it has been shown that generating adversarial counter examples that dispute this train/test split analysis is trivial~\cite{biggio_evasion_2013,carlini_towards_2017,adversarialpatch,pixelattack,hopskipjump,biggio_poisoning_2013,chakraborty_adversarial_2018,dohmatob_generalized_2019,meyers}. In addition, this method ignores the run-time cost of a given architectural decision, caring only for marginal accuracy gains on benchmark data~\cite{}. Instead, we can measure the computational feasibility of finding noisy counterexamples close to the original samples, such that 
$$
y\neq\hat{y}\mathrm{~s.t.~}\| x' - x \| \leq \varepsilon \leq \varepsilon_{max}
$$

where $\| \cdot \|$ represents some norm or pseudo-norm and $\varepsilon$ is some specified distance threshold bound by some distance, $\varepsilon_{max}$.

\subsubsection{Failure Rate}
 To encompass the cost of a particular model or attack, we can think of the failure rate as a function of time (\textit{e.g.} training time, inference time, attack generation time, etc.) and some covariates (\textit{e.g.} noise distance, model size, hardware resources) such that:
\[
h(t; \theta) :=  \frac{\mathbb{P}(\textrm{False~Classification})}{\Delta t}
\]
where $\mathbb{P}$ is a probability and $\Delta t$ is a time interval. To get a more precise and reliable estimate of a model's failure characteristics, we can use accelerated failure time models that model the \textbf{survival time}, $S(t)$, as a function of the samples, $x$, the labels, $y$, and some set of covariates, $\theta$ such that:
\[
S(t; x,y, \theta) := 1 - \int_{t=0}^{\infty} h(t;\theta) d \theta
\]

\subsection{AFR models}
\label{afr}
Accelerated failure rate models are statistical models used to analyze multivariate effects on the observed failure rate to predict the expected survival time ($\mathbb{E}[S(t; x,y, \theta)]$) across a wide variety of circumstances~\cite{aft_models,kleinbaum1996survival}. However, this requires a choice in modelling distribution for $S$. We tested Log-Logistic, Log-Normal, and Weibull distributions, relying on Akaike Information Criterion (AIC), Bayesian Information Criteria (BIC), and Concordance to choose the best-fit, following the best-practices of other research~\cite{aft_models}.  This analysis allows us to test the model under extreme perturbations, revealing not only the accuracy under ideal test scenarios, but to see the model's performance in the presence of noise that's designed to be adversarial. However, we still have to find optimal configurations for both the attack and defence, which often rely on parameters drawn from continuous or infinite spaces. In order to minimize the cost of evaluation, we must be clever about how we search.

\subsection{Pareto Set}
\cm{This section could probably be cut without too much lost.}
In security analysis, it is customary in security analysis to imagine a best-case scenario for both the defender and the attacker~\cite{}. A subset of examples that maximize one or more objective criteria is called the \textbf{pareto front}~\cite{zitzler2008quality}. It has been shown that we can find an $\varepsilon$-approximation of this front $\mathcal{P}$ in $d$ dimensions using $(1/ \varepsilon)^d$ queries ~\cite{legriel2010approximating}. Table~\ref{tab:pareto} shows the required number of queries to get estimates within the $\varepsilon$-sphere of the true Pareto front. As we can see, it is critical to minimize the dimensionality of our search. So instead of optimizing for latency, training time, cost, accuracy, and adversarial success rate independently, we introduce several metrics in the next section.

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{multirow}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{multirow}

@@

\section{Introduction}
\subsection{Motivations}
% \begin{itemize}
%     % \item \textit{BIG} Data is the trend
%     % \item Costs are astronomical
%     \item Prevailing regulatory framework is clear about the robustness requirements, documented software changes, and explainable processes.
%     \item Other work relies on unreliable test/train split methodology
%     \item Which means that cars, medical equipment is tested in the wild
% \end{itemize}

Recently, machine learning (ML) using neural networks has become a popular way to classify large amounts of data---with applications ranging from medical imaging~\cite{ai_medical_imaging} to aviation~\cite{ai_aviation} and from security~\cite{ai_security,ai_luggage,ai_prison} to self-driving cars~\cite{ai_automotive}. However, neural networks need large amounts of data\cite{desislavov2021compute,bailly2022effects} to train ever-larger model~\cite{desislavov2021compute}, yielding increasingly marginal gains on test-set accuracy~\cite{sun2017revisiting}. Furthermore, popular models like Generative Pre-trained Transformer (GPT)\cite{floridi2020gpt} or ResNet~\cite{resnet} have many millions of parameters, requiring equally large training datasets. Media reports place the cost of training a large language model somewhere between 4 and 63 million dollars~\cite{Patel_Ahmad_2023,Feswing_2023}, meaning only a few entities in the whole world have the requisite hardware and/or cloud budget to build a competing system. Facebook's large language model, dubbed LLaMA, was placed on the codesharing website, GitHub~\cite{llama}. Immediately, an open-sourced clone was created, which itself spawned hundreds of offshoot projects~\cite{openllama}. The newest version of this open-source large language model (LLM) is able to outperform the commercially available GPT-3.5 model with a fraction of the parameters (13 Billion), small enough to run on a laptop without a graphics processing unit (GPU)~\cite{liu2023goat}. Given the immense cost of deploying modern neural networks, the required number of test samples creates serious questions about the efficacy of the typical train/test split methodology for evaluating the ability of a model to generalize beyond a training set~\cite{meyers} since regulatory standards around safety-critical software applications~\cite{IEC61508,iso26262,aviation_software,safetyframework} clearly define the maximum failure rate to be between $[1e-12, 1e-15]$ depending on the number of lives at risk ~\cite{iso26262}. Collecting, labelling, and testing a new set of data for every software change-as required by law would be prohibitively expensive. Therefore, a new evaluation methodology is required. As such, we propose an evaluation metholodgy, centered around survival analysis, which tests a model against `worst-case' (e.g. adversarial) input to verify the efficacy of one of modelling deployment decision over another. Then, we use this method to examine and minimize the deployment cost for a single model architecture, measuring this in terms of both power and monetary cost. Furthermore, ensuring the robustness of ML models against adversarial noise has become a critical concern~\cite{adversarialpatch, carlini_towards_2017, croce_reliable_2020, hopskipjump, chakraborty2018adversarial, art2018}.

% \subsection{Research Questions}
% Our goal is to answer the following three questions:
% \begin{itemize}
%     \item What is the relationship between latency, robustness, and deployment cost?
%     \item What is the cheapest way to guarantee a certain response time and accuracy?
%     \item Does better hardware lead to better models?
% \end{itemize}

% However, before we can answer these questions, we need to model the asymptotic behavior of various architectural choices, develop a method for precisely measuring model performance without resorting to trillions of test samples, and find a metric (or metrics) that will set one model apart from the others with respect to both failure rate and deployment cost.

\subsection{Contributions}
So, in order to tackle the problems of minimizing deployment cost while maximizing the model performance on both the test set and in the presence of adversarial noise we present a scalable and effective technique and source code that:
\begin{itemize}
    \item confirm previous work about the efficacy of adversarial analysis for model selection,
    \item extend survival analysis to the realm of neural networks, 
    \item demonstrate a scalable and effective method that allows us to tune a model and model the effect of the model parameters asymptotically,
    \item and measure the power and monetary cost of deploying a model across three different hardware architectures to model the trade-offs between deployment hardware and robustness,
to show that, despite a decrease in training time, that faster hardware or hardware with more memory does not aid models in the adversarial context.

\end{itemize}

\section{Background}
ML pipelines play a crucial role in the development and deployment of robust and accurate models. However, managing complex pipelines across diverse CPU and GPU architectures, ensuring robustness against adversarial attacks, and understanding the relationship between computational cost, model loss, and prediction accuracy remain ongoing challenges. In this paper, we present a comprehensive study on leveraging Kubernetes~\cite{k8s} to manage a complex ML pipeline. We explore the robustness of the pipeline under adversarial attacks and examine the impact of computational cost on model performance in both benign and adversarial contexts.

ML applications have witnessed tremendous growth in recent years, addressing a wide range of domains and providing significant advancements in various fields \cite{li_general_2016, croce_reliable_2020, athalye_obfuscated_2018}. As these applications become more sophisticated, the need to efficiently manage the underlying ML pipeline arises. The pipeline involves a series of interconnected steps, including data preprocessing, model training, post-processing, and inference. Efficiently orchestrating these steps across diverse CPU and GPU architectures poses significant challenges in terms of scalability, resource allocation, and workload distribution.

To address these challenges, containerization and orchestration technologies have gained prominence in managing complex ML pipelines. Kubernetes, a widely adopted container orchestration platform, provides a scalable and flexible environment for deploying, scaling, and managing microservices-based applications. Its ability to handle heterogeneous hardware architectures and workload distribution across clusters makes it an ideal choice for managing the complex computational requirements of ML pipelines.

% Additionally, understanding the relationship between computational cost, model loss, and prediction accuracy is vital for optimizing the pipeline's performance. Balancing computational resources, time constraints, and accuracy requirements is a fundamental consideration in deploying ML models in production environments. By analyzing the impact of computational cost on model loss and accuracy metrics, we can gain insights into the trade-offs involved and make informed decisions to optimize the pipeline's efficiency.

In this paper, we present a comprehensive study that combines Kubernetes as the underlying infrastructure for managing a complex ML pipeline across a variety of GPU architectures. We can investigate the robustness of the pipeline against adversarial attacks and explore the relationship between computational cost, model loss, and  prediction accuracy in both benign and adversarial contexts. Our experiments and analysis provide valuable insights into the trade-offs and considerations when deploying ML models under varying computational constraints and adversarial conditions.

@@

\subsection{Cloud Architectures}
A \textit{microservice} is the smallest component of a `cloud-native' software stack. In the context of ML, that might be a tool for either training, inference, pre-processing, sampling, or any other arbitrarily small part of the data pipeline. A microservice \textit{mesh} is a network infrastructure or architectural pattern that provides a unified and scalable approach to managing communication between microservices in a distributed system. It serves as a dedicated layer that abstracts away the complexity of service-to-service communication, enabling efficient and reliable interactions among these services. A microservice mesh typically consists of a set of interconnected components or proxies deployed alongside the microservices within the system. These components facilitate various capabilities and functionalities essential for managing the communication between microservices. Kubernetes has become one of the largest open source projects on the code-sharing website Github \cite{k8s-size}, which provides a framework for managing, monitoring, and networking a self-scaling set of tools across arbitrary software and hardware architectures.

\subsection{ML Pipelines}
ML pipelines are often long-running and complex software tool-chains with many tunable hyperparameters. Managing, tracking, and controlling for various parameters is non trivial, but many management tools are available~\cite{dvc,hydra,k8s}. In general, a dataset is split into \textit{training} and \textit{test} sets. The training set is then used to determine the best configuration of a given model architecture on a given hardware architecture with the expectation that it will generalize both on the withheld test set and on new data generated and submitted by users. To verify the training process, the test set is validated against the \textit{inference} configuration of a model which may run on different hardware than the \textit{training} configuration to reduce cost, latency, or power consumption.

@@

A classifier, $K(x; \theta)$, with model parameters, $\theta$, drawn from a set of all possible hyper-parameters, $\Theta$, seeks to minimize\footnote{This can also be formulated as a maximization without loss of generality.} an \textit{objective} (or \textit{loss}) \textit{function} $L(y, \hat{y})$ for some samples, $x$, some true labels $y$, and some model output, $K(x)$, such that the optimal loss value, $L^*$ is:
\[
L^*(y, K(x, \theta)) = \mathrm{argmin}_{\theta \in \Theta} y - K(x, \theta).
\]
 In the case of neural networks, however, this is non-trivial as the number of tunable parameters is often measured in the millions and the loss function is non-convex. Instead of finding an analytical solution to this equation, we often rely on numerical optimisation, and one choice is \textit{stochastic gradient descent}, which samples the data before adjusting the model parameters, $\theta$, in the direction that minimizes the loss. This is in the direction of the negative gradient of the loss, $-\nabla L(y, K(x, \theta))$. This procedure is repeated for some number of \textit{epochs} (iteration through the entire training set), $m$, and every iteration thus performs the step,
\begin{equation}
    \theta_{m+1} = \theta_{m} - \eta \nabla_x L\big(y, K(x, \theta_m)\big),
\label{eq:sgd}
\end{equation}
where $\eta$ is a \textit{learning rate} that is tuned to the particular model.

\subsection{Learning Rate Selection}
\label{learning_rate}
Choosing the correct learning rate is critical for model performance---greatly effecting both the accuracy and the run-time requirements. A small learning rate will have a smaller error bound~cite{}, but will converge slower, all other things being equal. Of course `small` is arbitrarily defined, but the scale of the optimal learning rate will vary with \textit{e.g.}, the batch size, number of epochs, bit depth/size/scale of the input data. Graphics cards with larger amounts of RAM will be able to hold more data in memory at a time, increasing the effective batch size, and reducing the number of model-tuning steps per epoch. In theory, a `good' learning rate can converge quickly ~\cite{smith2019super} and the ideal batch size will be determined by the memory bandwidth of the GPU and the size, shape, and bit depth of the data. However, since cloud infrastructure is virutalized and shared with other users, the available bandwidth will not necessarily match the peak available bandwidth specified by the manufacturer~\cite{sajid2013cloud}. Furthermore, since hardware is billed by the hour, optimizing the training and inference times allows us to minimize the cost of deployment.

\subsection{Adversarial Attacks}
\label{attacks}
In the context of ML, an adversarial attack refers to deliberate and malicious attempts to manipulate or exploit ML models. Adversarial attacks are designed to deceive or change the model's behavior by introducing carefully crafted input data that can cause the model to make incorrect predictions or otherwise produce undesired outputs. That is, a successful attack is one in which the model outputs on the original, unperturbed data, $\hat{y}$, are not the same as the model outputs on perturbed data, $y'$. That is \textit{adversarial success} or \textit{accelerated failure} is one in which
\begin{equation}
    \hat{y} \neq y' = K(x + \varepsilon; \theta).
\label{eq:adv_success}
\end{equation}
Additionally, we can measure the accuracy of the model when tasked with these adversarial samples, giving us a metric called \textit{adversarial accurracy}. The goal of an adversarial attack is often to exploit vulnerabilities in the model's decision-making process or to probe its weaknesses. These attacks can occur during various stages of the ML pipeline, including during training, inference, or deployment, examples of which are outlined below.

\begin{itemize}
    \item Evasion Attacks: These attacks aim to manipulate input data during the inference phase to deceive the model into misclassifying certain inputs or otherwise change the behavior of a modelt~\cite{biggio_evasion_2013, carlini_towards_2017, adversarialpatch, pixelattack, hopskipjump}.
    % Attackers carefully craft perturbations or modify the input features to mislead the model while still appearing similar to the original input~\cite{biggio_evasion_2013, carlini_towards_2017, adversarialpatch, pixelattack, hopskipjump}.
    \item Poisoning Attacks: In poisoning attacks, the attacker intentionally injects malicious or manipulated training samples into the training dataset to influence the model's behaviour at run-time~\cite{biggio_poisoning_2013, saha2020hidden}. 
    % The goal is to influence the model's behavior during training so that it learns to make incorrect predictions or exhibit unwanted behaviors when presented with specific inputs \cite{biggio_poisoning_2013, saha2020hidden}.
    \item Inference Attacks: These attacks exploit the model's output or responses to obtain sensitive information about the training data or other confidential details~\cite{chakraborty_adversarial_2018, orekondy2019knockoff}.
    % By observing the model's predictions or confidence scores for carefully crafted inputs, attackers can extract information that should ideally be kept private \cite{chakraborty_adversarial_2018, orekondy2019knockoff}.
    \item Model Inversion Attacks: Model inversion attacks aim to infer sensitive information about the training data or proprietary model by exploiting the model's outputs~\cite{chakraborty_adversarial_2018, choquette2021label, li2021membership}. 
    % Attackers utilize the model's responses to iteratively reconstruct or approximate training examples that are similar to the ones used during training \cite{chakraborty_adversarial_2018, choquette2021label, li2021membership}.
\end{itemize}
One of many possible attacks is designed to induce failures as quickly as possible, and is  conveniently called the \textit{fast gradient method}~\cite{fgm}. It works by applying noise to a set of samples, $x$, to generate adversarial examples, $x'$, such that,
\begin{equation}
x' = x + \eta \cdot \mathrm{sign}(\nabla_x L(y, K(x, \theta))).
\label{eq:fgm}
\end{equation}
In essence, this is process seeks to maximize loss in contrast to model training which seeks to minimize it.

@@

In the case of safety- or security-critical domains, considering the worst-case scenario is routine~\cite{sajid2013cloud}. Whether we discuss automotive safety~\cite{ai_automotive}, crytographic systems~\cite{leurent2020sha,kamal2017study}, or healthcare malpractice~\cite{ai_medical_imaging}, a component, algorithm, or system is considered broken if the \textit{failure rate} exceeds a certain amount, depending the risk to human life~\cite{iso26262}. An order of magnitude more automotive accidents, security breaches, or deaths due to negligence would be unacceptable and, as such, these standards are non-negotiable. However, this would mean testing a million samples for every model change that has the potential to injure a human, with orders of magnitude more stringent requirement in the case of potentially fatal systems. This is just not computationally feasible. Instead, we can use adversarial failure analysis to improve the precision of our measurements while only using a small set of test-data.

\subsubsection{Accuracy}
The failure rate, denoted by $h$, refers to the percentage or proportion of examples that cause the targeted ML model to misclassify or produce incorrect outputs \cite{meyers}. It measures the vulnerability or susceptibility of the model to noise-induced failures. A higher failure rate indicates a higher rate of misclassifications or incorrect predictions, signifying a weaker model in terms of \textit{robustness} against noise-induced failures. Throughout, we use the terminology \textit{benign accuracy} to refer to the performance on the test set using unperturbed data. The benign accuracy is defined as
\begin{equation}
 \mathrm{Accuracy} = 1 - \frac{\mathrm{False~Classifications}}{\mathrm{Total~Classifciations}}
\label{eq:acc}
\end{equation}
which is generally assumed to indicate the rate of failures in real-world data drawn from the same distribution as the test data~\cite{tan2021critical}. However, the normal test/train split methodology consistently overestimates the model's performance in the presence of adversarial noise~\cite{croce_reliable_2020}. Additionally, it has been shown that generating adversarial counter examples that dispute this train/test split analysis is trivial~\cite{biggio_evasion_2013,carlini_towards_2017,adversarialpatch,pixelattack,hopskipjump,biggio_poisoning_2013,chakraborty_adversarial_2018,dohmatob_generalized_2019,meyers}. In addition,  ignores the run-time cost of a given architectural decision, caring only for marginal accuracy gains on benchmark data~\cite{desislavov2021compute,bailly2022effects}. Instead, we can measure the computational feasibility of finding noisy counterexamples close to the original samples, such that 
$$
    y\neq\hat{y}\text{~~while~~}\| x' - x \| \leq \varepsilon \leq \varepsilon_{max},
$$ 
where $\| \cdot \|$ represents some norm or pseudo-norm and $\varepsilon$ is some specified  perturbation distance threshold bound by a maximum distance, $\varepsilon_{max}$.

\subsubsection{Failure Rate}
 To encompass the cost of a particular model or attack, we can think of the failure rate as a function of time (\textit{e.g.}, training time, inference time, attack generation time, \textit{etc.}) and some covariates (\textit{e.g.}, noise distance, model size, hardware resources) such that,
\[
    h_{ \theta}(t) :=  \frac{P(\textrm{False~Classification})}{\Delta t} t
\]
where $P(\textrm{False~Classification})$ is the probability of a false classification and $\Delta t$ is a time interval. To get a more precise and reliable estimate of a model's failure characteristics, we can use accelerated failure time models that model the \textit{survival time}, $S(t)$, as a function of the time, $t$,  and some set of model parameters, $\theta$ such that,
\[
    S_{\theta}(t) := 1 - \int_{t=0}^{\infty} h_{\theta}(t) \,d\theta.
\]

\subsection{AFR models}
\label{afr}
Accelerated failure rate models are statistical models used to analyze multivariate effects on the observed failure rate to predict the expected survival time ($\mathbb{E}[S(t)]$) across a wide variety of circumstances~\cite{aft_models,kleinbaum1996survival}. However, this requires a choice in modelling distribution for $S$. We tested Log-Logistic, Log-Normal, and Weibull distributions, relying on Akaike Information Criterion (AIC), Bayesian Information Criteria (BIC), and Concordance to choose the best-fit, following the best-practices of this method~\cite{aft_models,kleinbaum1996survival}.  This analysis allows us to test the model under extreme perturbations, revealing not only the accuracy under ideal test scenarios, but to see the model's performance in the presence of noise that's designed to be adversarial. However, we still have to find optimal configurations for both the attack and defence, which often rely on parameters drawn from continuous or infinite spaces. In order to minimize the cost of evaluation, we must be clever about how we search.

% \subsection{Pareto Set}

% In security analysis, it is customary in security analysis to imagine a best-case scenario for both the defender and the attacker~\cite{kamal2017study,leurent2020sha}. A subset of examples that maximize one or more objective criteria is called the \textit{pareto front}~\cite{zitzler2008quality}. It has been shown that we can find an $\varepsilon$-approximation of this front $\mathcal{P}$ in $d$ dimensions using $(1/ \varepsilon)^d$ queries ~\cite{legriel2010approximating}. Table~\ref{tab:pareto} shows the required number of queries to get estimates within the $\varepsilon$-sphere of the true Pareto front. As we can see, it is critical to minimize the dimensionality of our search. So instead of optimizing for latency, training time, cost, accuracy, and adversarial success rate independently, we introduce several metrics in the next section.
